Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-11-20 manuscript_responses_v1.tex
fixed some updates

We also accordingly rewritten a couple of sentences in the Discussions presented in Section 7 and in the Conclusions of Section 8:
\begin{itemize}
\item In this case, sensitivity was measured using the correlation between the asymmetry parameter and the estimated RVs; {\bf{in the spot case SN median RV had a correlation with $\gamma$ as strong as the correlation between N mean RV and BIS SPAN (R=-0.81).}}
Moreover,  {\bf{when considering the case of a facula on the photosphere of the star}}, the correlation between the FWHM and the estimated RVs is stronger when using the parameters from the SN compared to the parameters from the Normal. {\bf{For the other presented cases, no statistically significant difference on the correlation between FWHM and the estimated RVs is obtained.}}

>>>>

We also accordingly rewritten a couple of sentences in the Discussions presented in Section 7 and in the Conclusions of Section 8:
\begin{itemize}
\item Sensitivity was measured using the correlation between the asymmetry parameter and the estimated RVs; {\bf{in the spot setting the SN median RV had a correlation with $\gamma$ as strong as the correlation between N mean RV and BIS SPAN (R= -0.81), and}}
{\bf{for the facula setting}}, the correlation between the FWHM and the estimated RVs is stronger when using the parameters from the SN compared to the parameters from the Normal. {\bf{For the spot and the spot plus a planet settings, no statistically significant difference on the correlation between FWHM and the estimated RVs were obtained.}}

### 2018-11-20 manuscript_v2_noiseSim.tex
fixed some updates

To evaluate the performance of the proposed SN framework, tests on both simulated and real data were carried out and compared to the commonly employed approach of fitting a Normal density shape (for estimating the RV and FWHM) and then separately deriving the BIS SPAN (for estimating the asymmetry).
The simulated CCFs were generated using the SOAP 2.0 code, which can simulate activity signals induced by a spot or a facula on a solar-like star. 
%The results of the simulation study suggest that the parameters derived from the SN density fit are more sensitive to activity than the parameters obtained by the usual Normal method, making them more useful indicators of activity.
%{\bf \color{red} The previous sentence is not correct; this was not demonstrated once the noise was added.]}
In this case, sensitivity was measured using the correlation between the asymmetry parameter and the estimated RVs; {\bf{in the spot case SN median RV had a correlation with $\gamma$ as strong as the correlation between N mean RV and BIS SPAN (R= -0.81).}}
Moreover,  {\bf{when considering the case of a facula on the photosphere of the star}}, the correlation between the FWHM and the estimated RVs is stronger when using the parameters from the SN compared to the parameters from the Normal. {\bf{For the other presented cases, no statistically significant difference on the correlation between FWHM and the estimated RVs is obtained.}}

>>>>

To evaluate the performance of the proposed SN framework, tests on both simulated and real data were carried out and compared to the commonly employed approach of fitting a Normal density shape (for estimating the RV and FWHM) and then separately deriving the BIS SPAN (for estimating the asymmetry).
The simulated CCFs were generated using the SOAP 2.0 code, which can simulate activity signals induced by a spot or a facula on a solar-like star. 
%The results of the simulation study suggest that the parameters derived from the SN density fit are more sensitive to activity than the parameters obtained by the usual Normal method, making them more useful indicators of activity.
%{\bf \color{red} The previous sentence is not correct; this was not demonstrated once the noise was added.]}
Sensitivity was measured using the correlation between the asymmetry parameter and the estimated RVs; {\bf{in the spot setting the SN median RV had a correlation with $\gamma$ as strong as the correlation between N mean RV and BIS SPAN (R= -0.81), and}}
{\bf{for the facula setting}}, the correlation between the FWHM and the estimated RVs is stronger when using the parameters from the SN compared to the parameters from the Normal. {\bf{For the spot and the spot plus a planet settings, no statistically significant difference on the correlation between FWHM and the estimated RVs were obtained.}}
